TBD

### 2016-10-13 paper.tex
improved CG section

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of only one major outer loop. It turns out that in the worst possible case 
the number of major iterations that is required by CG to converge is proportional to $\sqrt{\kappa}$.

The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

It should now be clear to
the reader why the CG method is espicially applicable to sparse linear systems, since in those cases $m < N^2$. 
We can improve the computational complexity of the CG method by preconditioning. 
[Preconditioning is a technique for improving the condition number of a matrix. Suppose that ' is a
symmetric, positive-definite matrix that approximates, but is easier to invert. We can solve indirectly by solving] - RW directly coppied from source
\begin{equation}
\bM^{-1}\bA\bx = \bM^{-1}\bb
\end{equation}

>>>>

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of only one major outer loop (line 6 of Algorithm \ref{algo:CG}). It turns out that at worst 
the number of major outer iterations that CG requires to converge\footnote{If the $\bA$-norm is used to calculate the error.} is proportional to $\sqrt{\kappa}$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ \citep{Lu2015}.
The mathematical definition of $\kappa(\bA)$ is
\begin{equation}
\label{eq:kappa}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ and $\lambda^{+}_{\textrm{min}}$ respectively denote the largest eigenvalue and the smallest positive eigenvalue of $\bA$.
Note that, since $\bA$ is positive-definite all its eigenvalues will be positive. The reason why it is required to spcifically add the positivity requirement to Eq.~\eqref{eq:kappa} will become
apparent after reading Sec \textbf{??}. Furthermore, the most expensive operation that is conducted within each major loop of Algorithm~\ref{algo:CG} is the vector-matrix product $\bA\bp$, which has a complexity of $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in $\bA$.
The computational complexity of CG is therefore 
\begin{equation}
\label{eq:cg_bound}
\mathbb{O}(\sqrt{\kappa}m). 
\end{equation}
It should now also be clear to the reader why the CG method is espicially applicable to sparse linear systems, since in those cases $m < P^2$.

\subsection{Preconditioning}
Preconditioning is a technique which allows us to improve the condition number of a matrix. Let $\bM$ be a positive-definite Hermitian matrix which approximates $\bA$.
Moreover, the inverse of $\bM$ must also be much easier to compute than the inverse of $\bA$. We can now indirectly solve for $\bx$ by using 
\begin{equation}
\label{eq:prec}
\bM^{-1}\bA\bx = \bM^{-1}\bb.
\end{equation}
The logic behind using Eq.~\eqref{eq:prec} rather than Eq.~\eqref{eq:linear_system} to obtain $\bx$ is that if $\bM$ is a good preconditioner then $\kappa(\bM^{-1}\bA) \ll \kappa(\bA)$, i.e.
by preconditioning we reduce $\kappa$ which improves the convergence rate of CG. The best choice of $\bM$ would be $\bA$, which would reduce $\kappa$ to unity which reduces
Eq.~\eqref{eq:cg_bound} to $\mathbb{O}(m)$. But of course, if we knew the inverse of $\bA$ then obtaining $\bx$ would be trivial and we would not need CG or any other type of 
linear solver for that mattter to compute it in the first place. If the diagonal entries of $\bA$ is much more significant than its off-diagonal entries then the 
Jacobian preconditioner is a good choice of $\bM$. The Jacobian preconditioner is computed as follows:
\begin{equation}
\bM = \bA\odot\bI, 
\end{equation}
where $\bI$ is the identity matrix. Since the Jacobian preconditioner is a diagonal matrix is inverse can be computed trivially.

Using preconditioning will therefore improve the 
, which 
implies that the computational complexity of the CG algorithm will be less in the case of  Eq.~\eqref{eq:prec} than in the case of Eq.~\eqref{eq:linear_system}.
